
\section{Outcomes and lessons learned}
\subsection{Outcomes}
\emph{I dont know wether this should be located here or is intended to be somewhere else}
The web-application we have developed has some limitations due to different reasons \textsl{reasons to come}. It does not do this and that and another feature we should have implemented is not functional at the moment. The features should be easy to add, because they were considered during system design and no interface changes have to be made.

Beside our final application we also produced some side products which are worth to be mentioned. These include but are not limited to:
\begin{itemize}
	\item junction
	\item bakery
	\item weave
	\item lego
\end{itemize}
\emph{to be explained asap (as short as possible) by someone who knows how to do that}

Additionally we produced a large amount of project- and other documentation. (Details here)

\subsection{Lessons learned}
%\emph{What each of us had learned technology wise and what we have learned about projects.}
For all of us this was the first project of this size and duration. We took the chance to put into practice what we had learned in our software engineering course. Especially things that are not applicable for smaller projects. Things like (list of things).

We had to learn, that project-oriented approaches are hard to adhere to in an educational setting. Our team could not meet as often as claimed by nearly all development methods. Nevertheless we managed to establish a systematic meeting shedule.

At the beginning the proposed architecture of our software changed often and radical. Even with a given set of written down requirements. This was due to hard to understand requirements. There where different interpretations of the described requirements. We got it right after the first phase mainly because of (why?).

Our present team had not worked together previous to this project. We experienced that we are very different people with different approaches to problems. Near to the end of this project we are all friends and doing stuff together in our freetime. Everyone learned to get along with the originalities of the others. We have to highlight, that respect and honesty are very important in a team to lead to a productive development environment.
%this project resulted in a lot of valuable experience on how to work in a team
%And with mutual cooperation, understanding, respect and helping each other, we successfully overcome all problems.

We had to undergo the experince, that a complex development environment has to be easy to set up. Otherwise it will consume a lot of time even after small changes to get ready to work again.
%By  self  learning,  knowledge  sharing  and  organizing  sessions  on  various  technology related issues we led our development process in a smooth and systematic manner.
%Moreover, there was less time for testing of project.

During  the  project  we  have  a  good  chance  to  learn  some  new  technologies
List of things we learned stated by the team members:
\begin{itemize}
	\item XML
\end{itemize}
